\section{Introduction}

\subsection{Business Context}
Customer churn is a critical issue for subscription-based telecom companies.
When customers leave, the business loses recurring revenue and may need to spend
additional resources to acquire replacement customers. A churn analysis report
should therefore help analysts and managers identify high-risk customer groups
and understand which customer attributes are associated with a higher churn
rate.

\subsection{Project Objectives}
The project has four objectives:
\begin{enumerate}
  \item Analyze customer churn patterns across customer, account, service, and
  experience dimensions.
  \item Compare churned and non-churned customers through exploratory data
  analysis.
  \item Build interpretable feature groups that support churn-rate comparison.
  \item Explain how course visualization techniques are applied to the final
  dashboard pages and summarize retention recommendations based on the observed
  signals.
\end{enumerate}

\subsection{Current Scope}
At this stage, this report is prepared as an Overleaf-compatible final report draft. It
contains the cover page, table of contents, dataset source, dataset statistics,
EDA plan, model workflow, expected insight narrative, and a technique
application section aligned with the course guideline in \code{guideline.md}.
The final dashboard screenshots are included from the group's final reporting
artifact in the \code{img/} folder. Not every recommended technique could be
implemented before submission, so the report distinguishes implemented design
choices from remaining future improvements.
