\section{Technique Application According to Course Guideline}

\subsection{Guideline Alignment}
The course guideline at
\url{https://datalab.vn/articles/2021-09/IT5425-quan-tri-du-lieu-va-truc-quan-hoa}
requires the report to explain which visualization techniques from the course
are applied to each relevant chart or page. It also requires the dataset to be
searchable through Google Dataset Search, which is already documented in the
dataset source section. This section follows that structure using the final
dashboard screenshots prepared by the group for reporting.

The technique mapping below uses the course guideline, the local course slides,
and the distilled note file
\code{Slide data viz/2024/notes/00\_distilled\_knowledge.md}. The most relevant
lectures are introduction to visualization, visual models and visual encoding,
graphical perception, table-data visualization, figure design, and storytelling
with data.

\begin{itemize}
  \item Introduction to data visualization.
  \item Visual model and visual encoding.
  \item Graphical perception.
  \item Visualization for table data.
  \item Principles of figure design.
  \item Storytelling with data.
\end{itemize}

\subsection{Reusable Technique-Application Template}
For each final chart or page, the report documents the design decision in the
following format:
\begin{itemize}
  \item \textbf{Chart/Page}: name of the final page or visual.
  \item \textbf{Technique / principle applied}: related course concept, such as
  visual encoding, common baseline, proportional ink, or storytelling.
  \item \textbf{How applied}: which variable is mapped to which mark, axis,
  color, or interaction.
  \item \textbf{Notes / adjustments}: limitations, denominator, or reason for
  not using another chart type.
\end{itemize}

Example: in a churn-rate-by-satisfaction chart, satisfaction groups should be
placed in ordinal order, churn rate should be encoded by bar length on a common
axis, and a 9.92\% baseline line should identify above-baseline groups. The
notes should state that these bars are within-group churn rates and therefore
are not expected to sum to 100\%.

\subsection{Chapter 1: Overview of Data Visualization}
\paragraph{Techniques / principles applied.}
The project uses visualization for both exploratory and explanatory purposes.
Exploratory charts help compare churned and non-churned customers across
feature groups. Explanatory charts communicate which groups are above or below
the baseline churn rate.

\paragraph{How applied in the dashboard.}
The final overview page starts with customer and churn KPIs, risk-level
distribution, selected-feature churn-rate comparison, and a signup-month trend.
This allows the audience to distinguish ``how many customers are in a group''
from ``how risky that group is''.

\paragraph{Notes / adjustments.}
The dataset is large and customer-level, so the dashboard should avoid showing
raw customer rows as the main view. Aggregated segment views are more suitable
for decision making.

\subsection{Chapter 2: Visual Models and Visual Encoding}
\paragraph{Techniques / principles applied.}
The selected variables cover several measurement levels: nominal variables
such as contract type and payment method, ordinal or discrete variables such as
customer satisfaction and complaint counts, and quantitative variables such as
monthly charges, average monthly GB, credit score, and days since last
interaction. The dashboard charts therefore use marks and channels that match
each variable type.

\paragraph{How applied in the dashboard.}
Bar marks should encode grouped categories. Position on a common axis and bar
length should encode counts and churn rates. Color hue should separate churn
from non-churn when both categories are shown, while a distinct highlight color
can mark groups whose churn rate is above the 9.92\% baseline.

\paragraph{Notes / adjustments.}
The report should avoid over-encoding. A chart should not use color, shape, and
size for the same distinction unless the redundancy improves accessibility.

\subsection{Chapter 3: Graphical Perception}
\paragraph{Techniques / principles applied.}
The design should prefer encodings that are easier to compare, especially
position and length. Preattentive color can guide attention to high-risk
groups. Gestalt principles such as proximity and similarity should group
related charts and filters.

\paragraph{How applied in the dashboard.}
For the EDA pages, customer-count bars and churn-rate bars should be placed near
each other for the same feature. Bars should share a consistent baseline so
that users can compare magnitudes accurately. Above-baseline churn groups should
be highlighted consistently across all feature pages.

\paragraph{Notes / adjustments.}
Color must not be the only signal for risk. Labels, baseline lines, and
consistent ordering should also indicate which groups are high risk.

\subsection{Chapter 4: Visualization for Table and Multidimensional Data}
\paragraph{Techniques / principles applied.}
The project mainly uses table-data visualization: amounts, distributions,
proportions, and relationships between grouped features and churn. The current
EDA plan separates customer distribution from churn risk.

\paragraph{How applied in the dashboard.}
Counts by churn status should use grouped bars. Churn rates by feature group
should use independent bar charts with the baseline churn rate as a reference
line. Numeric variables can use grouped bins, histograms, or box plots before
being summarized into business-readable groups. Relationships among multiple
features can be explored with filtered views or small multiples.

\paragraph{Notes / adjustments.}
Churn-rate bars across groups do not need to sum to 100\%. Each bar represents
the churn rate inside that group, not the share of total churn. Stacked bars
should only be used when the parts form a meaningful whole.

\subsection{Chapter 5 and Chapter 7: Graph and Map Visualization}
\paragraph{Techniques / principles applied.}
These chapters are not central to the current dataset because the data does not
contain explicit network edges or geographic locations.

\paragraph{How applied in the dashboard.}
No graph layout or map view is used in the current version.

\paragraph{Notes / adjustments.}
If the group later adds geographic or relationship data, this section should be
expanded with map encoding or graph-layout choices.

\subsection{Chapter 6: Principles of Figure Design}
\paragraph{Techniques / principles applied.}
The final figures are evaluated against proportional ink, clear titles and
captions, color accessibility, multi-panel consistency, and a balance between
data and context. Unnecessary 3D charts should be avoided.

\paragraph{How applied in the dashboard.}
Bars should start from zero when encoding counts or rates. Each chart should
include a title that states the analytical question, a y-axis label for the
metric, and a data-source note where appropriate. Multi-panel pages should keep
the same color mapping for churn and non-churn. Risk highlights should use a
colorblind-aware palette and direct labels when possible.

\paragraph{Notes / adjustments.}
The dataset is aggregated for visualization, so overlapping points are less of
a problem than in scatter plots. If scatter plots are added later, transparency,
binning, or sampling should be used to reduce overlap.

\subsection{Chapter 8: Interactive Visualization}
\paragraph{Techniques / principles applied.}
The relevant interaction techniques are filtering, selection, and view changes.
Animation is not required because the available dataset is not time-series
focused.

\paragraph{How applied in the dashboard.}
Users should be able to filter by contract type, tenure group, satisfaction
group, complaint group, service-call group, and payment behavior. Selecting a
segment should update both the distribution view and the churn-rate view so
that the effect of the filter is visible.

\paragraph{Notes / adjustments.}
Interactions should support comparison, not hide the baseline. The 9.92\%
overall churn-rate reference should remain visible whenever a filtered churn
rate is shown.

\subsection{Chapter 9: Storytelling with Data}
\paragraph{Techniques / principles applied.}
The report should move from context to evidence and then to action. The target
audience is a business or customer-retention team that needs to identify which
customer groups deserve attention.

\paragraph{How applied in the dashboard.}
The recommended narrative order is: introduce the churn problem, show the
baseline churn rate, compare churned and non-churned customers, identify the
strongest customer-experience signals, connect EDA with model outputs, and end
with retention recommendations.

\paragraph{Notes / adjustments.}
Each page should have a clear message title. The final version should replace
generic chart titles such as ``Churn by Feature'' with insight-oriented titles
such as ``Low satisfaction customers churn above the baseline'' when the
numbers support that statement.
